### 2014-11-10 Arvind.tex
stuff

We now turn our attention toward a more efficient implementation of
memory.  With the cache hierarchy of Figure~\ref{zoom}, we have concurrent
interaction of many processors with many caches
with main memory, and the relationship with the original $M_m$ system
is far from direct.  However, this intricate concurrent execution is
crucial to hiding the latency of main-memory access.
Figure~\ref{cache} formalizes as an LTS $M_c$ the algorithm we implemented,
for providing the memory abstraction on top of a cache hierarchy.
We have what is called an \emph{invalidating directory-based hierarchical
cache-coherence protocol}.  It is a transliteration of a realistic
algorithm~\cite{DNA:CoherenceImplementation} implemented in the
Bluespec hardware description language~\cite{Bluespec:TFRG}.

>>>>

We now turn our attention toward a more efficient implementation of
memory.  With the cache hierarchy of Figure~\ref{zoom}, we have concurrent
interaction of many processors with many caches, and the relationship with the original $M_m$ system
is far from direct.  However, this intricate concurrent execution is
crucial to hiding the latency of main-memory access.
Figure~\ref{cache} formalizes as an LTS $M_c$ the algorithm we implemented,
for providing the memory abstraction on top of a cache hierarchy.
We have what is called an \emph{invalidating directory-based hierarchical
cache-coherence protocol}.  It is a transliteration of a realistic
algorithm~\cite{DNA:CoherenceImplementation} implemented in the
Bluespec hardware description language~\cite{Bluespec:TFRG}.
